ps4_models

### 2020-10-29 bi-model.Rmd
asd

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)
library(brms)
```
```{r}
remove.packages("rstan")

@@

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_intention,
         vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         household_income,
         education
  )
reduced_data <- reduced_data[complete.cases(reduced_data), ]

@@

total_rows <- nrow(reduced_data)

@@

training <- data[0:boundary,]
model <- brms::brm(formula = vote_2020 ~ state + race_ethnicity + gender + 
                          household_income + education, 
                   data = training,
                   family = bernoulli(link = "logit"),
                   warmup = 500, 
                   iter = 4000, 
                   chains = 2, 
                   inits= "0", 
                   cores=2,
                   seed = 123
                   )
```

>>>>

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)
library(brms)
```
```{r}
# remove.packages("rstan")

@@

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_intention,
         vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         household_income,
         education
  )

reduced_data <- reduced_data[complete.cases(reduced_data), ]

@@

reduced_data <- droplevels(reduced_data)

total_rows <- nrow(reduced_data)
table(reduced_data$vote_2020)

@@

training <- data[0:boundary,]
model <- brm(formula = vote_2020 ~ (1|state) + (1|race_ethnicity) + (1|gender) + 
                          (1|household_income) + (1|education), 
             data = training,
             family = bernoulli(),

                   )
```

### 2020-10-29 multi-model.Rmd
asd

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)
library(brms)
```
```{r}
# remove.packages("rstan")

@@

```{r}
# install.packages("rstan", repos = "https://cloud.r-project.org/", dependencies = TRUE)

@@

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_intention,
         vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         household_income,
         education
  )

reduced_data <- reduced_data[complete.cases(reduced_data), ]

reduced_data <- reduced_data[reduced_data$vote_2020 == "Donald Trump" |
                             reduced_data$vote_2020 == "Joe Biden",]

@@

reduced_data <- droplevels(reduced_data)

total_rows <- nrow(reduced_data)
table(reduced_data$vote_2020)

reduced_data
```
```{r}
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.9)

training <- data[0:boundary,]
model <- brm(formula = vote_2020 ~ (1|state) + (1|race_ethnicity) + (1|gender) + 
                          (1|household_income) + (1|education), 
             data = training,
             family = bernoulli(),

                   )
```

@@

probability <- predict(model, newdata = training, "probs")
column_index <- max.col(probability, tie="random")

testing_predictions <- colnames(probability)[column_index]
testing_ground_truth <- training %>% pull(vote_2020)
accuracy(testing_ground_truth, testing_predictions)

>>>>

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)

@@

<!-- ```{r} -->
<!-- raw_data <- read_dta("inputs/data/usa_00001.dta") -->
<!-- # Add the labels -->
<!-- raw_data <- labelled::to_factor(raw_data) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Just keep some variables that may be of interest (change  -->
<!-- # this depending on your interests) -->
<!-- names(raw_data) -->

<!-- reduced_data <-  -->
<!--   raw_data %>%  -->
<!--   select( -->
<!--          stateicp, -->
<!--          sex, -->
<!--          race,  -->
<!--          educd, -->
<!--          inctot) -->

<!-- head(reduced_data) -->
<!-- reduced_data$race %>% table() -->
<!-- reduced_data$stateicp %>% table() -->
<!-- reduced_data$educd %>% table() -->
<!-- reduced_data$sex %>% table() -->
<!-- reduced_data$inctot %>% table() -->

<!-- strat <- reduced_data -->
<!-- ``` -->

@@

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_intention,
         vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         household_income,
         education
  )
reduced_data <- reduced_data[complete.cases(reduced_data), ]

@@

total_rows <- nrow(reduced_data)

```
```{r}
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.9)

training <- data[0:boundary,]
model <- nnet::multinom(vote_2020 ~ state + race_ethnicity + gender + 
                          education, data = training)
```

@@

probability <- predict(model, newdata = testing, "probs")
column_index <- max.col(probability, tie="random")

testing_predictions <- colnames(probability)[column_index]
testing_ground_truth <- testing %>% pull(vote_2020)
accuracy(testing_ground_truth, testing_predictions)
